\bf Title here

### 2020-07-10 paper/paper.tex
modify notation as per wednesday meeting (16)

The optimisation problem we're interested in is in the context of
projection pursuit. Coined by \citet{friedman1974projection}, projection
pursuit is a method that detects the interesting structure
(i.e.~clustering, outliers and skewness) of multivariate data via
projecting it in lower dimensions. Let \(\mathbf{D}_{n \times p}\) be a
data matrix, an n-d projection can be seen as a linear transformation:
\(T: \mathbb{R}^p \mapsto \mathbb{R}^d\) defined by
\(\mathbf{P} = \mathbf{D} \cdot \mathbf{A}\), where
\(\mathbf{P}_{n \times p}\) is the projected data and
\(\mathbf{A}_{p\times d}\) is the projection basis Define
\(f: \mathbb{R}^{p \times d} \mapsto \mathbb{R}\) be an index function
that maps the projection basis \(\mathbf{A}\) onto a scalar value \(I\),
this function is commonly known as the projection pursuit index (PPI)
function, or index function and can be used to measure the
``interestingness'' of the projection. A number of indice functions have
been proposed in the literature and this includes Legendre index
\citep{friedman1974projection}, hermite index
\citep{hall1989polynomial}, natural hermite index
\citep{cook1993projection}, chi-square index
\citep{posse1995projection}, LDA index \citep{lee2005projection} and PDA
index \citep{lee2010projection}. {[}Any literature on holes index?
xxx{]}

@@

\begin{align}
&\arg \max_{\mathbf{A} \in \mathcal{A}} f(\mathbf{A}) \\
s.t. & \mathcal{A} = \{ \forall \mathbf{a}_i \in \mathbf{A}: \lVert \mathbf{a}_i \rVert = 1 \}
\end{align}

via an iterative search:
\(\{\mathbf{A}^j: \mathbf{A}^1, \mathbf{A}^2, \cdots \cdots \mathbf{A}^J\}\).
Guided tour interpolates geodesically between each basis found by
projection pursuit \(A^j\) to form a tour path:
\[\{ \mathbf{A}^0, \mathbf{A}^1, {}_{1}\mathbf{A}^1, {}_{2}\mathbf{A}^1,\cdots, {}_{k_1}\mathbf{A}^1, A^2, {}_{1}\mathbf{A}^2, {}_{2}\mathbf{A}^2, \cdots {}_{k_2}\mathbf{A}^2, \cdots, \mathbf{A}^{J-1}, {}_{1}\mathbf{A}^{J-1}, \cdots {}_{k_m}\mathbf{A}^{J-1} ,\mathbf{A}^J \}\]

@@

Now we formulate the idea of global object using mathmetical notation.
Let \(\mathbf{A}^0\) denotes the starting basis. Superscript \(j\) is
used to denote the number of iteration (index per iteration). Candidate
basis are denoted using subscript on the right and interpolation basis
are denoted using subscript on the left. For example,
\(\mathbf{A}^1_{2}\) means the second candidate basis in the first
iteration and \({}_{2}\mathbf{A}^1\) means the second interpolation
basis that forms the tour path from the current basis \(\mathbf{A}^0\)
to the target basis \(\mathbf{A}^1\). In iteration two, \(\mathbf{A}^1\)
becomes the current basis and projection pursuit searches through
\(\mathbf{A}^2_{1}, \mathbf{A}^2_{2}, \cdots, \mathbf{A}^2_{l_2}\) to
find the target basis \(\mathbf{A}^2\). The tour path from
\(\mathbf{A}^1\) to \(\mathbf{A}^2\) is constructed using the
interpolation bases
\({}_{1}\mathbf{A}^2, {}_{2}\mathbf{A}^2, \cdots, {}_{k_2}\mathbf{A}^2\).
All the bases together can be arranged in a format that each coloumn
represents an iteration as in Equation \ref{eq:matrixA}.

\begin{equation}
\left[
\begin{array}{ccccccc}
/ & \mathbf{A}^1_1 & \mathbf{A}^2_1 & \cdots & \mathbf{A}^j_1 &\cdots & \mathbf{A}^J_1 \\
/ & \mathbf{A}^1_2 & \mathbf{A}^2_2 & \cdots & \mathbf{A}^j_2 &\cdots & \mathbf{A}^J_2 \\
\vdots & \vdots & \vdots & \ddots & \vdots & \ddots &\vdots   \\
/ &\mathbf{A}^1_{l_1} & \mathbf{A}^2_{l_2} & \cdots & \mathbf{A}^j_{l_h} &\cdots & \mathbf{A}^J_{L_H}\\
\hline
\mathbf{A}^0 & \mathbf{A}^1 & \mathbf{A}^2 & \cdots & \mathbf{A}^j  &\cdots & \mathbf{A}^J\\
\hline
/ &{}_{1}\mathbf{A}^1 & {}_{1}\mathbf{A}^2 & \cdots &{}_{1}\mathbf{A}^j & \cdots & /\\
/ &{}_{2}\mathbf{A}^1 & {}_{2}\mathbf{A}^2 & \cdots &{}_{2}\mathbf{A}^j & \cdots & / \\
\vdots & \vdots & \vdots & \ddots & \vdots  & \ddots & / \\
/ &{}_{k_1}\mathbf{A}^1 & {}_{k_2}\mathbf{A}^2 & \cdots &{}_{k_m}\mathbf{A}^j & \cdots & / \\
\end{array}
\right]
= 
\left[
\begin{array}{c}
\vphantom{A^J_1}\text{candidate basis} \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{A^J_{L_H}}\text{candidate basis} \\
\hline
\vphantom{A^J}\text{output basis} \\
\hline
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\vdots \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\end{array}
\right]
\label{eq:matrixA}
\end{equation}

@@

\begin{equation}
\begin{bsmallmatrix}
\mathbf{A}^0 &\mathbf{A}^1_1 &  \mathbf{A}^1_{2} & \cdots& \mathbf{A}^1_{l_1} & \mathbf{A}^1 & {}_{1}\mathbf{A}^1& {}_{2}\mathbf{A}^1 &\cdots& {}_{k_1}\mathbf{A}^1 & \mathbf{A}^2_1 & \mathbf{A}^2_{2} & \cdots& \mathbf{A}^2_{l_2} & \mathbf{A}^2 & {}_{1}\mathbf{A}^2 &{}_{2}\mathbf{A}^2 &\cdots& {}_{k_2}\mathbf{A}^2 & \cdots & \mathbf{A}^J
\end{bsmallmatrix} 
\label{eq:vectorA}
\end{equation}

\begin{equation}
\left[
\begin{array}{c|c|ccc|ccc}
\mathbf{A}^0 & I^0 & 0 & / & 1 & / & \cdots & /\\
\hline
\mathbf{A}^1_1 & I^1_1 & 1 & 1 & 2 & o_{1, 1} & \cdots & o_{p, 1}\\
\mathbf{A}^1_2 & I^1_2 & 1 & 2 & 3 & o_{1, 2} & \cdots & o_{p, 2}\\
\vdots &\vdots & \vdots &\vdots &\vdots &\vdots &\cdots &\vdots\\
\mathbf{A}^1_{l_1} & I^1_{l_1} & 1 & l_1 & l_1+1 & \vdots & \cdots & \vdots\\
\hline 
\mathbf{A}^1 & I^1 & 1 & l_1 + 1 & l_1 + 2 & \vdots & \cdots & \vdots\\
\hline
{}_{1}\mathbf{A}^1 &{}_{1}I^1 & 1 & / & l_1 + 3 &\vdots & \cdots & \vdots\\
{}_{2}\mathbf{A}^1 &{}_{2}I^1 & 1 & / & l_1 + 4&\vdots & \cdots & \vdots\\
\vdots &\vdots &\vdots  &\vdots &\vdots &\vdots &\cdots &\vdots \\
{}_{k_1}\mathbf{A}^1 &{}_{k_1}I^1 & 1 & / & l_1 +k_1 + 2 &\vdots & \cdots & \vdots\\
\hline
\vdots &\vdots &\vdots  &\vdots &\vdots &\vdots &\cdots &\vdots \\
\mathbf{A}^J_{l_H} & I^J_{l_H} & J & l_H & n-1 &o_{1, n-1}& \cdots & o_{p, n-1}\\
\mathbf{A}^J & I^J & J & l_H + 1 & n & o_{1, n}& \cdots & o_{p, n}\\
\end{array}
\right]
\label{eq:data-structure}
\end{equation}

where \(n = (J-1) + \sum_{h = 1}^H l_h + \sum_{m = 1}^M k_m + 1\)

>>>>

The optimisation problem we're interested in is in the context of
projection pursuit. Coined by \citet{friedman1974projection}, projection
pursuit is a method that detects the interesting structure
(i.e.~clustering, outliers and skewness) of multivariate data via
projecting it in lower dimensions. Let \(\mathbf{X}_{n \times p}\) be a
data matrix, an n-d projection can be seen as a linear transformation:
\(T: \mathbb{R}^p \mapsto \mathbb{R}^d\) defined by
\(\mathbf{P} = \mathbf{X} \cdot \mathbf{A}\), where
\(\mathbf{P}_{n \times p}\) is the projected data and
\(\mathbf{A}_{p\times d}\) is the projection basis Define
\(f: \mathbb{R}^{p \times d} \mapsto \mathbb{R}\) be an index function
that maps the projection basis \(\mathbf{A}\) onto a scalar value \(I\),
this function is commonly known as the projection pursuit index (PPI)
function, or index function and can be used to measure the
``interestingness'' of the projection. A number of indice functions have
been proposed in the literature and this includes Legendre index
\citep{friedman1974projection}, hermite index
\citep{hall1989polynomial}, natural hermite index
\citep{cook1993projection}, chi-square index
\citep{posse1995projection}, LDA index \citep{lee2005projection} and PDA
index \citep{lee2010projection}. {[}Any literature on holes index?
xxx{]}

@@

\begin{align}
&\arg \max_{\mathbf{A} \in \mathcal{A}} f(\mathbf{A}) \\
s.t. & \mathcal{A} = \{ \forall \mathbf{a}_i, \mathbf{a}_j \in \mathbf{A}: \lVert \mathbf{a}_i \rVert = 1 \text{ and } \mathbf{a}_i \mathbf{a}_j = 0 \}
\end{align}

via an iterative search:
\(\{\mathbf{A}^1, \mathbf{A}^2, \cdots \cdots \mathbf{A}^J\}\). Guided
tour interpolates geodesically between each basis found by projection
pursuit \(A^j\) to form a tour path:
\[\{ \mathbf{A}^0, \mathbf{A}^1, {}_{1}\mathbf{A}^1, {}_{2}\mathbf{A}^1,\cdots, {}_{k_1}\mathbf{A}^1, A^2, {}_{1}\mathbf{A}^2, {}_{2}\mathbf{A}^2, \cdots {}_{k_2}\mathbf{A}^2, \cdots, \mathbf{A}^{J-1}, {}_{1}\mathbf{A}^{J-1}, \cdots {}_{k_m}\mathbf{A}^{J-1} ,\mathbf{A}^J \}\]

@@

Now we formulate the idea of global object using mathmetical notation.
Let \[\mathbf{A}_{j,l,k}\] denotes the projection matrix in iteration
\(j\). If it is searching basis produced in the optimisation, then it
has a subscript \(l\). If it is an interpolation basis, it has a \(k\)
subscript. For example \(\mathbf{A}_{1,2,/}\) means the second searching
basis in the first iteration, \(\mathbf{A}_{1, /, 2}\) means the second
interpolation basis that on the tour path from the current basis
\(\mathbf{A}^0\) to the target basis found in iteration 1:
\(\mathbf{A}^1\). The target basis found in each iteration,
\(\mathbf{A}_{j, l_j, /}\) can also be simplified using a superscript as
\(\mathbf{A}^j\).

Let \(\mathbf{A}^0\) denotes the starting basis. Superscript \(j\) is
used to denote the number of iteration (index per iteration). Candidate
basis are denoted using subscript on the right and interpolation basis
are denoted using subscript on the left. For example,
\(\mathbf{A}^1_{2}\) means the second candidate basis in the first
iteration and \({}_{2}\mathbf{A}^1\) means the second interpolation
basis that forms the tour path from the current basis \(\mathbf{A}^0\)
to the target basis \(\mathbf{A}^1\). In iteration two, \(\mathbf{A}^1\)
becomes the current basis and projection pursuit searches through
\(\mathbf{A}^2_{1}, \mathbf{A}^2_{2}, \cdots, \mathbf{A}^2_{l_2}\) to
find the target basis \(\mathbf{A}^2\). The tour path from
\(\mathbf{A}^1\) to \(\mathbf{A}^2\) is constructed using the
interpolation bases
\({}_{1}\mathbf{A}^2, {}_{2}\mathbf{A}^2, \cdots, {}_{k_2}\mathbf{A}^2\).
All the bases together can be arranged in a format that each coloumn
represents an iteration as in Equation \ref{eq:matrixA}.

\begin{equation}
\left[
\begin{array}{ccccccc}
\ast & \mathbf{A}_{1,1,\ast} & \mathbf{A}_{2, l_1 +1,\ast} & \cdots & \mathbf{A}_{j,\sum_{i = 1}^{j-1}l_i +1,\ast} &\cdots & \mathbf{A}_{J,\sum_{i = 1}^{J-1}l_i +1 ,\ast} \\
\ast & \mathbf{A}_{1,2,\ast} & \mathbf{A}_{2,l_1 +2,\ast} & \cdots & \mathbf{A}_{j,\sum_{i = 1}^{j-1}l_i +2,\ast} &\cdots & \mathbf{A}_{J,\sum_{i = 1}^{J-1}l_i +2, \ast} \\
\vdots & \vdots & \vdots & \ddots & \vdots & \ddots &\vdots   \\
\ast & \mathbf{A}_{1, l, \ast} & \mathbf{A}_{2, l_1 + l, \ast} & \cdots & \mathbf{A}_{j, \sum_{i = 1}^{j-1}l_i + l, \ast}  &\cdots & \mathbf{A}_{J, \sum_{i = 1}^{J-1}l_i + l, \ast}\\
\vdots & \vdots & \vdots & \ddots & \vdots & \ddots &\vdots   \\
\mathbf{A}_{0,\ast,\ast} & \mathbf{A}_{1, l_1, \ast} & \mathbf{A}_{2, l_1 + l_2, \ast} & \cdots & \mathbf{A}_{j, \sum_{i = 1}^{j}l_i , \ast}  &\cdots & \mathbf{A}_{J, \sum_{i = 1}^{J} l_i, \ast}\\
\hline
\ast &\mathbf{A}_{1, \ast, 1} & \mathbf{A}_{2, \ast, k_1 + 1} & \cdots &\mathbf{A}_{j, \ast,\sum_{i = 1}^{j-1}k_i + 1} & \cdots & \ast\\
\ast &\mathbf{A}_{1, \ast, 2} & \mathbf{A}_{2, \ast, k_1 + 2} & \cdots &\mathbf{A}_{j, \ast, \sum_{i = 1}^{j-1}k_i +2} & \cdots & \ast \\
\vdots & \vdots & \vdots & \ddots & \vdots  & \ddots & \vdots \\
\ast &\mathbf{A}_{1, \ast, k} & \mathbf{A}_{2, \ast, k_1 + k} & \cdots &\mathbf{A}_{j, \ast, \sum_{i = 1}^{j-1}k_i +k} & \cdots & \ast \\
\vdots & \vdots & \vdots & \ddots & \vdots  & \ddots & \vdots \\
\ast &\mathbf{A}_{1, \ast, k_1} & \mathbf{A}_{2, \ast, k_1 + k_2} & \cdots &\mathbf{A}_{j, \ast,\sum_{i = 1}^{j}k_i} & \cdots & \ast \\
\end{array}
\right]
= 
\left[
\begin{array}{c}
\vphantom{A^J_1}\text{candidate basis} \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{A^J_2}\text{candidate basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{A^J}\text{current/target basis} \\
\hline
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\text{NULL}}\vdots \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\vphantom{\vdots} \vdots \\
\vphantom{\text{NULL}}\text{interpolation basis} \\
\end{array}
\right]
\label{matrixA}
\end{equation}

@@

All the basis can also be denoted usign a single subscript by their
natural ordering as
\(\mathbf{A}_0, \mathbf{A}_1, \cdots, \mathbf{A}_n\).

\begin{equation}
\begin{array}{cccccccc}
\bigl[\mathbf{A}_{0, \ast, \ast} & 
\mathbf{A}_{1, 1, \ast} & 
\mathbf{A}_{1,2,\ast} & 
\cdots & 
\mathbf{A}_{1,l,\ast} & 
\cdots & 
\mathbf{A}_{1,l_1, \ast}   \\ 
\mathbf{A}_{1, \ast, 1} & 
\mathbf{A}_{1, \ast, 2} & 
\cdots &
\mathbf{A}_{1, \ast, k} &
\cdots &
\mathbf{A}_{1, \ast, k_1} &
\cdots &
\mathbf{A}_{J, l_J, \ast} \bigr]
\end{array} 
\label{eq:vectorA}
\end{equation}

\begin{equation}
\left[
\begin{array}{c|c|cccc|ccc}
\mathbf{A} & I & j &  l  & k & n & S_{1}& \cdots & S_{p}\\
\hline
\mathbf{A}_0 & I_0 & 0 & \ast & \ast & 1 & \ast & \cdots & \ast\\
\hline
\mathbf{A}_1 & I_1 & 1 & 1 & \ast& 2 & S_{1, 1} & \cdots & S_{p, 1}\\
\mathbf{A}_2 & I_2 & 1 & 2 &\ast & 3 & S_{1, 2} & \cdots & S_{p, 2}\\
\vdots &\vdots & \vdots &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots\\
\vdots & \vdots & 1 & l_1 & \ast & \vdots & \vdots & \cdots & \vdots\\
\hline
\vdots & \vdots & 1 & \ast & 1& \vdots &\vdots & \cdots & \vdots\\
\vdots &\vdots& 1 & \ast & 2& \vdots&\vdots & \cdots & \vdots\\
\vdots &\vdots &\vdots  &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots \\
\vdots &\vdots & 1 & \ast & k_1&\vdots &\vdots & \cdots & \vdots\\
\hline
\vdots &\vdots &\vdots  &\vdots & \vdots &\vdots &\vdots &\cdots &\vdots \\
\mathbf{A}_n & I_n & J &  l_J & \ast & n & S_{1, n}& \cdots & S_{p, n}\\
\end{array}
\right]
\label{eq:data-structure}
\end{equation}

where \(n = 1+ \sum_{i = 1}^J l_i + \sum_{i = 1}^{J-1} k_i\)
